---
title: "CaseStudy2"
output: html_document
Authors: Evan Adams, Ryan Paul
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(caret)
```
## Summary
We are DDSAnalytics, an analytics company that specializes in talent management solutions for Fortune 1000 companies. We were hired by a large beer conglomerate to analyze employee data to come up with a model to predict employee attrition.

## Pulling in the data
```{r importData, message=FALSE}
#Import data
dfTrain <- read.csv("CaseStudy2-data.csv")
dfVal <- read.csv("CaseStudy2Validation.csv")
```

## Getting data ready for analysis
```{r arrangingData}
#Dropping the following columns so we don't have to copy and paste the code dropping the columns in the analysis every time
# ID & Rand: Are arbitrary
# Over18, StandardHours, and EmployeeCount: Only have one level
dfTrainModified <- dfTrain %>%
  select(-c(Over18, ID, StandardHours, EmployeeCount, Rand)) %>%
  na.omit() %>%
  as.data.frame()

dfValModified <- dfVal %>%
  select(-c(Over18, ID, StandardHours, EmployeeCount, Rand)) %>%
  na.omit() %>%
  as.data.frame()

# Force Attrition to be a factor column for the binomial analysis
dfTrainModified$Attrition <- factor(dfTrainModified$Attrition)
dfValModified$Attrition <- factor(dfValModified$Attrition)

# View the integers used
contrasts(dfTrainModified$Attrition)
```

## Stepwise analysis
```{r stepwiseAnalysis}
# Creating a model with all columns, binomial means it's a logistic regression, or regression with only two outcomes
# In our case employees either quit or they didn't
attritionModel.fit = glm(Attrition ~ ., data=dfTrainModified, family=binomial)

# Using Stepwise model selection to determine parameters to include in the overall formula
stepwiseGlmAnalysis <- step(attritionModel.fit, direction="both")

# Summary 
summary(stepwiseGlmAnalysis)
```

## Formula we will use
```{r returnedFormula}
formula(stepwiseGlmAnalysis)
```

## Testing formula against training set
```{r selfTesting}
# Use the model found with stepwise selection to give predictions
attrition.probability = predict(glm(formula(stepwiseGlmAnalysis), data=dfTrainModified, family=binomial), dfTrainModified, type="response")

# Make a vector of "No"
attrition.predicted = rep("No", dim(dfTrainModified)[1])

# Convert predicted values of greater than .5 to "Yes"
attrition.predicted[attrition.probability > .5] = "Yes"

# How did we do?
confusionMatrix(table(attrition.predicted,dfTrainModified$Attrition))
```

## Using model to create the test set we are to return
```{r testOnDfVal}
attritionValidate.probability = predict(glm(formula(stepwiseGlmAnalysis), data=dfValModified, family=binomial), dfValModified, type="response")

# Make a vector of "No"
attritionValidate.predicted = rep("No", dim(dfValModified)[1])

# Convert predicted values of greater than .5 to "Yes"
attritionValidate.predicted[attritionValidate.probability > .5] = "Yes"

# How did we do?
confusionMatrix(table(attritionValidate.predicted,dfValModified$Attrition))
```

## Create CSV Deliverable
```{r finalPredictionDeliverable}
# Creating the new dataframe that will be written
# Keeping Attrition in there to do one last test
dfPreds = data.frame(dfVal[,c("ID", "Attrition")], attritionValidate.predicted)
names(dfPreds) <- c("ID","Attrition", "AttritionPredicted")

# Write the final deliverable
write.csv(dfPreds[,c("ID", "AttritionPredicted")], "Case2PredictionsAdams_Paul.csv", row.names = FALSE)
```

## Itemized Accuracy
### Predicted Yeses that were Nos
```{r itemizedAccuracy}
dfJustNo <- dfPreds %>%
  filter(Attrition == "No") %>%
  as.data.frame()

countFalsePositive <- dfJustNo %>%
  filter(AttritionPredicted == "Yes") %>%
  as.data.frame()

dim(countFalsePositive)[1] / dim(dfJustNo)[1]
```

### Predicted Nos that were Yeses
```{r NosThatWereYeses}
dfJustYes <- dfPreds %>%
  filter(Attrition == "Yes") %>%
  as.data.frame()

countMissedTurnover <- dfJustYes %>%
  filter(AttritionPredicted == "No") %>%
  as.data.frame()

dim(countMissedTurnover)[1] / dim(dfJustYes)[1]
```

## Github Repo
https://github.com/eta2sec/MSDS6306_CaseStudy2

## Video for Ryan Paul
https://www.youtube.com/watch?v=QPIQIiiNq8Q

## Video for Evan Adams
